Attributes-based Object Classification and Segmentation

### 2010-05-11 trunk/paper.tex
updated paper

\title{Segmentation Using Attributes}

\author{Aibo Tian\\
%Institution1\\
%Institution1 address\\
{\tt\small atian@cs.utexas.edu}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
\and
John Edwards\\
%Institution2\\
%First line of institution2 address\\
{\tt\small edwardsj@cs.utexas.edu}
}

@@

%-------------------------------------------------------------------------------
% related work
%-------------------------------------------------------------------------------
\section{Related work}
\label{sec:related_work}
A significant amount of recent work has been done in the area of using
attributes as high-level features for image classification and object
description \cite{farhadi09, lampert09, kumar09}.
Another area of computer vision, that of segmentation,
has seen a resurgence of popularity as methods to incorporate top-down
information into segmentation have been shown to be highly effective
\cite{borenstein04, pantofaru, gu09, russell06, malisiewicz, leibe04, hoiem05, shotton06}.
We propose to leverage research done in both of these areas -- attributes
and top-down/bottom-up segmentation -- to produce a combined approach.

@@

@@

Attributes are high-level features which can reflect semantic properties of objects. Given the attributes, we can do object detection based on the their distribution. We use the same attribute set as \cite{farhadi09}. This set contains three types of attributes, including shape, part and material. All attributes are listed in figure \ref{fig:atts}.

@@

In this section, we evaluate our attribute based object detection
and segmentation algorithm. We will answer four questions. (1) What
is the performance of object detection and segmentation? (2) What are
the influences of different parameters? (3) What are the advantages
of the two pruning algorithms? (4) Is vertical confidence
propagation useful? (In this draft, we only have partial results, so
not all the questions are considered.)

%\subsection{Dataset}
%\label{ssec:dataset}

We use the Pascal2008 dataset. This dataset has a lot of real life
images which are more difficult to classify. The objects are labeled
by bounding boxes not accurate segmentation. For training the
attributes, we use the pascal2008 training set. The attribute
annotations used in \cite{farhadi09} are freely available and we
used them for training too. For testing the classification and
segmentation, we use the pascal2008 validation set. We plan to do
three classes classification and segmentation, including car,
aeroplane and horse. Now we only got the results on car. We will
incorporate the other classes in the final version.

Table \ref{table:aresults} shows some of the results from running
the additive algorithm on all cars in the dataset.  The recall is
the rate of correctly detecting images with cars.  The segmentation
precision is calculated with
\[ V(M_{groundtruth},M_{pred}) = \frac{|M_{groundtruth} \cap M_{pred}|}{|M_{groundtruth} \cup M_{pred}|} \]
where $M_{groundtruth}$ is the groundtruth mask calculated from the
bounding boxes stored with the annotations and $M_{pred}$ is the
predicted segmentation mask.  We of course recognize that the
bounding boxes are not a good measure of segmentation truth, but
it's the best we have available.

The segmentation precision for the additive algorithm
is far better than the precision for the subtractive algorithm (which averaged
0.09).  This is because the additive algorithm only segments images for
which it has predicted presence of a car, so that any image pruned by the
algorithm already has a high car similarity score, enhancing the segmentation.
The subtractive algorithm, on the other hand, assumes presence of a car in
the image and proceeds no matter how poor the initial similarity score is.
(For the final paper we expect to have results comparing the precision
of the two algorithms based only on images segmented by both.)

Figures \ref{fig:good_results} and \ref{fig:bad_results} show the
results of segmentations of various images by both pruning
algorithms. Figure \ref{fig:good_results} shows some good results,
while Figure \ref{fig:bad_results} shows some bad results. This
shows clear linkage between prominence of the side profile of the
car and success of the segmentation. It appears that the attribute
classifiers are more accurate on side profiles than front and rear
shots, although rear shots performed reasonably well when tail
lights were not illuminated.

@@

\begin{figure*}[p]
\centering
\begin{tabular}{ p{4cm} p{4cm} p{4cm} p{4cm} }
\includegraphics[width=3.95cm]{figures/results/2008_000052.jpg.eps} &
\includegraphics[width=3.95cm]{figures/results/2008_000828.jpg.eps} &
\includegraphics[width=3.95cm]{figures/results/2008_000952.jpg.eps} &
\includegraphics[width=3.95cm]{figures/results/2008_002198.jpg.eps} \\
\includegraphics[width=3.95cm]{figures/results/a2008_000052.jpg.eps} &
\includegraphics[width=3.95cm]{figures/results/a2008_000828.jpg.eps} &
\includegraphics[width=3.95cm]{figures/results/a2008_000952.jpg.eps} &
\includegraphics[width=3.95cm]{figures/results/a2008_002198.jpg.eps} \\
\includegraphics[width=3.95cm]{figures/results/b2008_000052.jpg.eps} &
\includegraphics[width=3.95cm]{figures/results/b2008_000828.jpg.eps} &
\includegraphics[width=3.95cm]{figures/results/b2008_000952.jpg.eps} &
\includegraphics[width=3.95cm]{figures/results/b2008_002198.jpg.eps} \\
\end{tabular}
\caption{Selected results from segmentation of cars from the Pascal2008
dataset.  The first row shows the original image.  The second row shows
the best segmentation from the additive algorithm.  The third row shows
the segmentation from the subtractive algorithm with $f=0.9$.}
\label{fig:good_results}
\end{figure*}

\begin{figure*}[p]
\centering
\begin{tabular}{ p{4cm} p{4cm} p{4cm} p{4cm} }
\includegraphics[width=3.95cm]{figures/results/2008_002483.jpg.eps} &
\includegraphics[width=3.95cm]{figures/results/2008_007466.jpg.eps} &
\includegraphics[width=3.95cm]{figures/results/2008_005378.jpg.eps} &
\includegraphics[width=3.95cm]{figures/results/2008_007529.jpg.eps} \\
\includegraphics[width=3.95cm]{figures/results/a2008_002483.jpg.eps} &
\includegraphics[width=3.95cm]{figures/results/a2008_007466.jpg.eps} &
%\includegraphics[width=3.95cm]{figures/results/a2008_005378.jpg.eps} &
Car not detected &
\includegraphics[width=3.95cm]{figures/results/a2008_007529.jpg.eps} \\
\includegraphics[width=3.95cm]{figures/results/b2008_002483.jpg.eps} &
\includegraphics[width=3.95cm]{figures/results/b2008_007466.jpg.eps} &
\includegraphics[width=3.95cm]{figures/results/b2008_005378.jpg.eps} &
\includegraphics[width=3.95cm]{figures/results/b2008_007529.jpg.eps} \\
\end{tabular}
\caption{Selected results from segmentation of cars from the Pascal2008
dataset.  The first row shows the original image.  The second row shows
the best segmentation from the additive algorithm.  The third row shows
the segmentation from the subtractive algorithm with $f=0.9$.}
\label{fig:bad_results}
\end{figure*}

\begin{figure*}[p]
\centering
\begin{tabular}{ p{4cm} p{4cm} p{4cm} p{4cm} }
\includegraphics[width=3.95cm]{figures/add_res/car/2008_007064.jpg.eps} &
\includegraphics[width=3.95cm]{figures/add_res/car/2008_000052.jpg.eps} &
\includegraphics[width=3.95cm]{figures/add_res/car/2008_007171.jpg.eps} &
\includegraphics[width=3.95cm]{figures/add_res/car/2008_000251.jpg.eps} \\
\includegraphics[width=3.95cm]{figures/add_res/car/2008_007064.jpg_1_good.jpg.eps} &
\includegraphics[width=3.95cm]{figures/add_res/car/2008_000052.jpg_1_good.jpg.eps} &
\includegraphics[width=3.95cm]{figures/add_res/car/2008_007171.jpg_1_good.jpg.eps} &
\includegraphics[width=3.95cm]{figures/add_res/car/2008_000251.jpg_1_good.jpg.eps} \\
\end{tabular}
\caption{Selected results from segmentation of cars from the Pascal2008
dataset.  The first row shows the original image.  The second row shows
the best segmentation from the additive algorithm.  The third row shows
the segmentation from the subtractive algorithm with $f=0.9$.}
\label{fig:good_results_car}
\end{figure*}

\begin{figure*}[p]
\centering
\begin{tabular}{ p{4cm} p{4cm} p{4cm} p{4cm} }
\includegraphics[width=3.95cm]{figures/add_res/car/2008_000868.jpg.eps} &
\includegraphics[width=3.95cm]{figures/add_res/car/2008_000884.jpg.eps} &
\includegraphics[width=3.95cm]{figures/add_res/car/2008_001830.jpg.eps} &
\includegraphics[width=3.95cm]{figures/add_res/car/2008_001867.jpg.eps} \\
\includegraphics[width=3.95cm]{figures/add_res/car/2008_000868.jpg_1_bad.jpg.eps} &
\includegraphics[width=3.95cm]{figures/add_res/car/2008_000884.jpg_1_bad.jpg.eps} &
\includegraphics[width=3.95cm]{figures/add_res/car/2008_001830.jpg_1_bad.jpg.eps} &
\includegraphics[width=3.95cm]{figures/add_res/car/2008_001867.jpg_1_bad.jpg.eps} \\
\end{tabular}
\caption{Selected results from segmentation of cars from the Pascal2008
dataset.  The first row shows the original image.  The second row shows
the best segmentation from the additive algorithm.  The third row shows
the segmentation from the subtractive algorithm with $f=0.9$.}
\label{fig:good_results_car}
\end{figure*}

\begin{figure*}[p]
\centering
\begin{tabular}{ p{4cm} p{4cm} p{4cm} p{4cm} }
\includegraphics[width=3.95cm]{figures/add_res/plane/2008_000021.jpg.eps} &
\includegraphics[width=3.95cm]{figures/add_res/plane/2008_001971.jpg.eps} &
\includegraphics[width=3.95cm]{figures/add_res/plane/2008_002673.jpg.eps} &
\includegraphics[width=3.95cm]{figures/add_res/plane/2008_002138.jpg.eps} \\
\includegraphics[width=3.95cm]{figures/add_res/plane/2008_000021.jpg_2_good.jpg.eps} &
\includegraphics[width=3.95cm]{figures/add_res/plane/2008_001971.jpg_2_good.jpg.eps} &
\includegraphics[width=3.95cm]{figures/add_res/plane/2008_002673.jpg_2_good.jpg.eps} &
\includegraphics[width=3.95cm]{figures/add_res/plane/2008_002138.jpg_2_good.jpg.eps} \\
\end{tabular}
\caption{Selected results from segmentation of cars from the Pascal2008
dataset.  The first row shows the original image.  The second row shows
the best segmentation from the additive algorithm.  The third row shows
the segmentation from the subtractive algorithm with $f=0.9$.}
\label{fig:good_results_car}
\end{figure*}

\begin{figure*}[p]
\centering
\begin{tabular}{ p{4cm} p{4cm} p{4cm} p{4cm} }
\includegraphics[width=3.95cm]{figures/add_res/plane/2008_000804.jpg.eps} &
\includegraphics[width=3.95cm]{figures/add_res/plane/2008_001805.jpg.eps} &
\includegraphics[width=3.95cm]{figures/add_res/plane/2008_002358.jpg.eps} &
\includegraphics[width=3.95cm]{figures/add_res/plane/2008_003673.jpg.eps} \\
\includegraphics[width=3.95cm]{figures/add_res/plane/2008_000804.jpg_2_bad.jpg.eps} &
\includegraphics[width=3.95cm]{figures/add_res/plane/2008_001805.jpg_2_okay.jpg.eps} &
\includegraphics[width=3.95cm]{figures/add_res/plane/2008_002358.jpg_2_okay.jpg.eps} &
\includegraphics[width=3.95cm]{figures/add_res/plane/2008_003673.jpg_2_bad.jpg.eps} \\
\end{tabular}
\caption{Selected results from segmentation of cars from the Pascal2008
dataset.  The first row shows the original image.  The second row shows
the best segmentation from the additive algorithm.  The third row shows
the segmentation from the subtractive algorithm with $f=0.9$.}
\label{fig:good_results_car}
\end{figure*}

\begin{figure*}[p]
\centering
\begin{tabular}{ p{4cm} p{4cm} p{4cm} p{4cm} }
\includegraphics[width=3.95cm]{figures/add_res/horse/2008_001542.jpg.eps} &
\includegraphics[width=3.95cm]{figures/add_res/horse/2008_001992.jpg.eps} &
\includegraphics[width=3.95cm]{figures/add_res/horse/2008_002172.jpg.eps} &
\includegraphics[width=3.95cm]{figures/add_res/horse/2008_002509.jpg.eps} \\
\includegraphics[width=3.95cm]{figures/add_res/horse/2008_001542.jpg_3_good.jpg.eps} &
\includegraphics[width=3.95cm]{figures/add_res/horse/2008_001992.jpg_3_good.jpg.eps} &
\includegraphics[width=3.95cm]{figures/add_res/horse/2008_002172.jpg_3_good.jpg.eps} &
\includegraphics[width=3.95cm]{figures/add_res/horse/2008_002509.jpg_3_good.jpg.eps} \\
\end{tabular}
\caption{Selected results from segmentation of cars from the Pascal2008
dataset.  The first row shows the original image.  The second row shows
the best segmentation from the additive algorithm.  The third row shows
the segmentation from the subtractive algorithm with $f=0.9$.}
\label{fig:good_results_car}
\end{figure*}

\begin{figure*}[p]
\centering
\begin{tabular}{ p{4cm} p{4cm} p{4cm} p{4cm} }
\includegraphics[width=3.95cm]{figures/add_res/horse/2008_000403.jpg.eps} &
\includegraphics[width=3.95cm]{figures/add_res/horse/2008_002835.jpg.eps} &
\includegraphics[width=3.95cm]{figures/add_res/horse/2008_003055.jpg.eps} &
\includegraphics[width=3.95cm]{figures/add_res/horse/2008_004470.jpg.eps} \\
\includegraphics[width=3.95cm]{figures/add_res/horse/2008_000403.jpg_3_bad.jpg.eps} &
\includegraphics[width=3.95cm]{figures/add_res/horse/2008_002835.jpg_3_bad.jpg.eps} &
\includegraphics[width=3.95cm]{figures/add_res/horse/2008_003055.jpg_3_okay.jpg.eps} &
\includegraphics[width=3.95cm]{figures/add_res/horse/2008_004470.jpg_3_bad.jpg.eps} \\
\end{tabular}
\caption{Selected results from segmentation of cars from the Pascal2008
dataset.  The first row shows the original image.  The second row shows
the best segmentation from the additive algorithm.  The third row shows
the segmentation from the subtractive algorithm with $f=0.9$.}
\label{fig:good_results_car}
\end{figure*}

>>>>

\title{Attributes-based Object Classification and Segmentation}

\author{Aibo Tian and John Edwards\\
University of Texas at Austin\\
%Institution1\\
%Institution1 address\\
{\tt\small \{atian,edwardsj\}@cs.utexas.edu}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
%\and
%John Edwards\\
%Institution2\\
%First line of institution2 address\\
%{\tt\small edwardsj@cs.utexas.edu}
%University of Texas at Austin\\
}
%University of Texas at Austin\\

@@

%-------------------------------------------------------------------------------
% related work
%-------------------------------------------------------------------------------
\section{Related work}
\label{sec:related_work}

A significant amount of recent work has been done in the area of using
attributes as high-level features for image classification and object
description \cite{farhadi09, lampert09, kumar09}.
Another area of computer vision, that of segmentation,
has seen a resurgence of popularity as methods to incorporate top-down
information into segmentation have been shown to be highly effective
\cite{borenstein04, pantofaru, gu09, russell06, malisiewicz, leibe04, hoiem05, shotton06}.
We propose to leverage research done in both of these areas -- attributes
and top-down/bottom-up segmentation -- to produce a combined approach.

@@

%\begin{figure}
%\centering
%\includegraphics[width=0.5\textwidth]{figures/flowchart.eps}
%\caption{Flowchart of the proposed algorithm.} \label{fig:flowchart}
%\end{figure}

@@

Attributes are high-level features which can reflect semantic properties of objects. Given the attributes, we can do object detection based on their distribution. We use the same attribute set as \cite{farhadi09}. This set contains three types of attributes, including shape, part and material. All attributes are listed in figure \ref{fig:atts}.

@@

In this section, we evaluate our attribute based object classification
and segmentation algorithm. We will also analyse the advantages and disadvantages of out algorithm.\\

\subsection{Dataset}
\label{ssec:dataset}

We use the Pascal2008 dataset for both training and testing. This dataset has a lot of real life
images which are more difficult to classify. The objects are labeled
by bounding boxes not accurate segmentation. For training the
attributes, we use the pascal2008 training set. The attribute
annotations used in \cite{farhadi09} are freely available and we
used them for training too. For testing the classification and
segmentation, we use the pascal2008 validation set. Three classes are used in this experiment, including car,
aeroplane and horse. We get 328 testing images, with car 150, aeroplane 103 and horse 93. Note that one image 
can contain multiple objects in multiple classes.\\

\subsection{Measure}
\label{ssec:measure}

For object classification, we use precision and recall to measure the performance. 
For segmentation, we use the ratio of intersection and union of the prediction and 
groundtruth as the measure of precision. The segmentation
precision is calculated with
\[ V(M_{groundtruth},M_{pred}) = \frac{|M_{groundtruth} \cap M_{pred}|}{|M_{groundtruth} \cup M_{pred}|} \]
where $M_{groundtruth}$ is the groundtruth mask calculated from the
bounding boxes stored with the annotations and $M_{pred}$ is the
predicted segmentation mask.  We of course recognize that the
bounding boxes are not a good measure of segmentation truth, but
it's the best we have available.\\

\subsection{Classification}
\label{ssec:classification}

Table \ref{table:aresults} shows the classification results comparing the proposed method with 
the other three baseline methods. LowFea means that we use the low level feature to train and test 
the object classification directly. Att1 means that we use the attribute distribution as the feature,
but we only test it in the whole image without segmentation. Random means random prediction. Add is our
proposed algorithm with additive pruning. The proposed algorithm has the highest precision comparing 
with the other baselines, while the recall is a little lower than LowFea. Figure \ref{fig:roc_class} 
shows the ROC curve for each class and the average.\\

@@

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{figures/add_res/roc_class.png.eps}
\caption{Result of adjusting the factor $f$ in the subtractive
algorithm. \subref{fig:fa} shows running the algorithm with $f=0.9$
and \subref{fig:fb} shows running the algorithm with $f=1.0$.  Note
that \subref{fig:fb} retains more of the cars, especially the two
closest on the right and left, but also has more false-positive
pixels, such as the ceiling region of the parking garage.}
\label{fig:roc_class}
\end{figure}

\subsection{Segmentation}
\label{ssec:segmentation}

Figure \ref{fig:roc_seg} shows the segmentation precision of additive pruning 
versus the false positive rate of object classification. The segmentation precision
is in the range of $20\%$ to $50\%$. Some of the segmentation results are shown in 
Figure \ref{fig:car_good_results},\ref{fig:car_bad_results},\ref{fig:aeroplane_good_results},\ref{fig:aeroplane_bad_results},\ref{fig:horse_good_results},\ref{fig:horse_bad_results}.\\

Figures \ref{fig:car_good_results} and \ref{fig:car_bad_results} show the
segmentations of car images by both additive and subtractive pruning
algorithms. Figure \ref{fig:good_results} shows some good results,
while Figure \ref{fig:bad_results} shows some bad results. This
shows clear linkage between prominence of the side profile of the
car and success of the segmentation. It appears that the attribute
classifiers are more accurate on side profiles than front and rear
shots, although rear shots performed reasonably well when tail
lights were not illuminated.\\

Figures \ref{fig:aeroplane_good_results}, \ref{fig:aeroplane_bad_results} and 
\ref{fig:horse_good_results}, \ref{fig:horse_bad_results} show some good and bad 
segmentation results of additive algorithm on aeroplane and horse classes. Because of the
high complexity of the subtractive algorithm, we did not run it on these two classes. The good 
results are accurate to segment out the objects. One important note is that our algorithm can segment out
multiple objects at the same time. The bad segmentations either miss 
part of the object or contain so much background. The bad ones are caused 
by two reasons. First, the hierarchical segmentation tree is not fine enough. We did not use all 
levels in the segmentation tree. The more levels we use, the more time we need to spend on it. 
Also when the segments are too small, the attribute detection is nearly random, because the small regions 
do not have enough points to represent their properties. Second, the training of attributes based on
bounding boxes is not accurate, because of many background pixels can be included in the bounding boxes. 
This is especially obvious to the horse images, since horses are not convex enough in the images. 
All the segmented images in figure \ref{fig:horse_bad_results} contains grass or trees, especially the 
left one which only contains grass. These images prove that the grass or trees models are actually
included in the horse model.\\

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{figures/add_res/roc_seg.png.eps}
\caption{Result of adjusting the factor $f$ in the subtractive
algorithm. \subref{fig:fa} shows running the algorithm with $f=0.9$
and \subref{fig:fb} shows running the algorithm with $f=1.0$.  Note
that \subref{fig:fb} retains more of the cars, especially the two
closest on the right and left, but also has more false-positive
pixels, such as the ceiling region of the parking garage.}
\label{fig:roc_seg}
\end{figure}

%\begin{figure*}[p]
%\centering
%\begin{tabular}{ p{4cm} p{4cm} p{4cm} p{4cm} }
%\includegraphics[width=3.95cm]{figures/results/2008_000052.jpg.eps} &
%\includegraphics[width=3.95cm]{figures/results/2008_000828.jpg.eps} &
%\includegraphics[width=3.95cm]{figures/results/2008_000952.jpg.eps} &
%\includegraphics[width=3.95cm]{figures/results/2008_002198.jpg.eps} \\
%\includegraphics[width=3.95cm]{figures/results/a2008_000052.jpg.eps} &
%\includegraphics[width=3.95cm]{figures/results/a2008_000828.jpg.eps} &
%\includegraphics[width=3.95cm]{figures/results/a2008_000952.jpg.eps} &
%\includegraphics[width=3.95cm]{figures/results/a2008_002198.jpg.eps} \\
%\includegraphics[width=3.95cm]{figures/results/b2008_000052.jpg.eps} &
%\includegraphics[width=3.95cm]{figures/results/b2008_000828.jpg.eps} &
%\includegraphics[width=3.95cm]{figures/results/b2008_000952.jpg.eps} &
%\includegraphics[width=3.95cm]{figures/results/b2008_002198.jpg.eps} \\
%\end{tabular}
%\caption{Selected results from segmentation of cars from the Pascal2008
%dataset.  The first row shows the original image.  The second row shows
%the best segmentation from the additive algorithm.  The third row shows
%the segmentation from the subtractive algorithm with $f=0.9$.}
%\label{fig:good_results}
%\end{figure*}

%\begin{figure*}[p]
%\centering
%\begin{tabular}{ p{4cm} p{4cm} p{4cm} p{4cm} }
%\includegraphics[width=3.95cm]{figures/results/2008_002483.jpg.eps} &
%\includegraphics[width=3.95cm]{figures/results/2008_007466.jpg.eps} &
%\includegraphics[width=3.95cm]{figures/results/2008_005378.jpg.eps} &
%\includegraphics[width=3.95cm]{figures/results/2008_007529.jpg.eps} \\
%\includegraphics[width=3.95cm]{figures/results/a2008_002483.jpg.eps} &
%\includegraphics[width=3.95cm]{figures/results/a2008_007466.jpg.eps} &
%\includegraphics[width=3.95cm]{figures/results/a2008_005378.jpg.eps} &
%Car not detected &
%\includegraphics[width=3.95cm]{figures/results/a2008_007529.jpg.eps} \\
%\includegraphics[width=3.95cm]{figures/results/b2008_002483.jpg.eps} &
%\includegraphics[width=3.95cm]{figures/results/b2008_007466.jpg.eps} &
%\includegraphics[width=3.95cm]{figures/results/b2008_005378.jpg.eps} &
%\includegraphics[width=3.95cm]{figures/results/b2008_007529.jpg.eps} \\
%\end{tabular}
%\caption{Selected results from segmentation of cars from the Pascal2008
%dataset.  The first row shows the original image.  The second row shows
%the best segmentation from the additive algorithm.  The third row shows
%the segmentation from the subtractive algorithm with $f=0.9$.}
%\label{fig:bad_results}
%\end{figure*}

\begin{figure*}[p]
\centering
\begin{tabular}{ p{3cm} p{3cm} p{3cm} p{3cm} }
\includegraphics[width=2.95cm]{figures/add_res/car/2008_007064.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/car/2008_000052.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/car/2008_007171.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/car/2008_000251.jpg.eps} \\

\includegraphics[width=2.95cm]{figures/add_res/car/2008_007064.jpg_1_good.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/car/2008_000052.jpg_1_good.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/car/2008_007171.jpg_1_good.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/car/2008_000251.jpg_1_good.jpg.eps} \\

\includegraphics[width=2.95cm]{figures/sub_results/2008_007064_1_bad_sub.jpg.eps} &
\includegraphics[width=2.95cm]{figures/sub_results/2008_000052_1_bad_sub.jpg.eps} &
\includegraphics[width=2.95cm]{figures/sub_results/2008_007171_1_bad_sub.jpg.eps} &
\includegraphics[width=2.95cm]{figures/sub_results/2008_000251_1_bad_sub.jpg.eps} \\
\end{tabular}
\caption{Selected results from segmentation of cars from the Pascal2008
dataset.  The first row shows the original image.  The second row shows
the best segmentation from the additive algorithm.  The third row shows
the segmentation from the subtractive algorithm with $f=0.9$.}
\label{fig:car_good_results}
\end{figure*}

\begin{figure*}[p]
\centering
\begin{tabular}{ p{3cm} p{3cm} p{3cm} p{3cm} }
\includegraphics[width=2.95cm]{figures/add_res/car/bad/2008_001961.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/car/bad/2008_003132.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/car/bad/2008_004312.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/car/bad/2008_004414.jpg.eps} \\

\includegraphics[width=2.95cm]{figures/add_res/car/bad/2008_001961.jpg_1_bad.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/car/bad/2008_003132.jpg_1_bad.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/car/bad/2008_004312.jpg_1_bad.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/car/bad/2008_004414.jpg_1_bad.jpg.eps} \\

\includegraphics[width=2.95cm]{figures/sub_results/good/2008_001961_0.80.jpg.eps} &
\includegraphics[width=2.95cm]{figures/sub_results/good/2008_003132_1.10.jpg.eps} &
\includegraphics[width=2.95cm]{figures/sub_results/good/2008_004312_1.00.jpg.eps} &
\includegraphics[width=2.95cm]{figures/sub_results/good/2008_004414_0.90.jpg.eps} \\

\end{tabular}
\caption{Selected results from segmentation of cars from the Pascal2008
dataset.  The first row shows the original image.  The second row shows
the best segmentation from the additive algorithm.  The third row shows
the segmentation from the subtractive algorithm with $f=0.9$.}
\label{fig:car_bad_results}
\end{figure*}

\begin{figure*}[p]
\centering
\begin{tabular}{ p{3cm} p{3cm} p{3cm} p{3cm} }
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_000021.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_001971.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_002673.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_002138.jpg.eps} \\
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_000021.jpg_2_good.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_001971.jpg_2_good.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_002673.jpg_2_good.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_002138.jpg_2_good.jpg.eps} \\
\end{tabular}
\caption{Selected results from segmentation of cars from the Pascal2008
dataset.  The first row shows the original image.  The second row shows
the best segmentation from the additive algorithm.  The third row shows
the segmentation from the subtractive algorithm with $f=0.9$.}
\label{fig:aeroplane_good_results}
\end{figure*}

\begin{figure*}[p]
\centering
\begin{tabular}{ p{3cm} p{3cm} p{3cm} p{3cm} }
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_000804.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_001805.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_002358.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_003673.jpg.eps} \\
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_000804.jpg_2_bad.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_001805.jpg_2_okay.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_002358.jpg_2_okay.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_003673.jpg_2_bad.jpg.eps} \\
\end{tabular}
\caption{Selected results from segmentation of cars from the Pascal2008
dataset.  The first row shows the original image.  The second row shows
the best segmentation from the additive algorithm.  The third row shows
the segmentation from the subtractive algorithm with $f=0.9$.}
\label{fig:aeroplane_bad_results}
\end{figure*}

\begin{figure*}[p]
\centering
\begin{tabular}{ p{3cm} p{3cm} p{3cm} p{3cm} }
\includegraphics[width=2.95cm]{figures/add_res/horse/2008_001542.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/horse/2008_001992.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/horse/2008_002172.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/horse/2008_002509.jpg.eps} \\
\includegraphics[width=2.95cm]{figures/add_res/horse/2008_001542.jpg_3_good.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/horse/2008_001992.jpg_3_good.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/horse/2008_002172.jpg_3_good.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/horse/2008_002509.jpg_3_good.jpg.eps} \\
\end{tabular}
\caption{Selected results from segmentation of cars from the Pascal2008
dataset.  The first row shows the original image.  The second row shows
the best segmentation from the additive algorithm.  The third row shows
the segmentation from the subtractive algorithm with $f=0.9$.}
\label{fig:horse_good_results}
\end{figure*}

\begin{figure*}[p]
\centering
\begin{tabular}{ p{3cm} p{3cm} p{3cm} p{3cm} }
\includegraphics[width=2.95cm]{figures/add_res/horse/2008_000403.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/horse/2008_002835.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/horse/2008_003055.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/horse/2008_004470.jpg.eps} \\
\includegraphics[width=2.95cm]{figures/add_res/horse/2008_000403.jpg_3_bad.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/horse/2008_002835.jpg_3_bad.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/horse/2008_003055.jpg_3_okay.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/horse/2008_004470.jpg_3_bad.jpg.eps} \\
\end{tabular}
\caption{Selected results from segmentation of cars from the Pascal2008
dataset.  The first row shows the original image.  The second row shows
the best segmentation from the additive algorithm.  The third row shows
the segmentation from the subtractive algorithm with $f=0.9$.}
\label{fig:horse_bad_results}
\end{figure*}
